### 2016-09-30 paper/conclusions_v1.tex
renamed paper tex files so that we can do latexdiff on them

\chapter{Conclusion} \label{chap:conc}

In this chapter we summarize the main contributions of the thesis and discuss future work.

%------------------------------------------------------------%
\section{Thesis Summary} 
%------------------------------------------------------------%

The contribution of this work is an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters. We applied this method to pairs of models, one that differed in the physics included and one that differed in the space to which the parameters belonged. In both cases, we were able to obtain a value for the QoI with a small relative error without having to solve the inverse problem with the high-fidelity model. In these cases, the element-wise decomposition of the error estimate also indicated regions of the parameter field that were both informed by the observations and informative to the QoI.

The inverse problem with the high-fidelity models examined were not so expensive to solve as to warrant the adaptive formation of a mixed-fidelity model; however, based on existing work with concurrent multi-fidelity models, savings in computational cost are expected in cases where the high-fidelity model is more complex and solving the inverse problem with the high-fidelity model is less tractable. We demonstrated a case where the inverse problem with the high-fidelity model could not be solved without a more complex nonlinear solver, but where our method resulted in a mixed-fidelity model for which the inverse problem could be solved with a simple nonlinear solver, with a small relative error in the QoI.

@@

An immediate direction for extension of this work is to the case of the statistical inverse problem. Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization. However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}. One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.

A popular approach to solving the statistical inverse problem is to apply a Bayesian framework. Bayes' rule is used to combine a prior distribution, which captures prior beliefs about the parameters, and a likelihood distribution, which captures the likelihood of observations given an instance of the parameter values and a model of noise in the observations, to give a posterior distribution on the parameters. Since there is generally no analytical expression for this posterior distribution, it is usually characterized by samples from the distribution. Sampling methods like the widely-used Markov chain Monte Carlo (MCMC) method require many evaluations of the forward model, and since the number of samples needed grows exponentially with the dimension of the parameter space, this problem becomes intractable for large parameter spaces. In engineering contexts, it is still usually the case, however, that we are ultimately interested in a low-dimensional QoI, and it is the uncertainty in this low-dimensional quantity that we wish to capture; this low-dimensional distribution is referred to as the predictive posterior.

One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled. Such a direction is suggested by the results presented in Section \ref{sec:constvfield}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space. In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution. In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed. Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.

@@

%soil chapter in Multiscale Modeling: A Bayesian Perspective - seems to do hierachical multiscale in context of mcmc
%http://arxiv.org/pdf/1402.1694v3.pdf has pointers to where people use surrogate models to avoid evaluating forward model too often...

%read http://www.stat.osu.edu/~comp_exp/jour.club/KennedyOHagan2000.pdf for the lulz?

%stochastic
%anything in chad's about curse of dimensionality?
%wolfgang bangert -> mesh refinement and stochastic, keep coarse sometimes...see if this might be related to extension?
	%can't seem to find anything by him related to this...at least, not suggested by title...
%matt parno or patrick's stuff? exploring with surrogate models mostly and then upping fidelity strategically?

%poke stochastic weak form? is that another way we could think about extending to stochastic case?

>>>>

\section{Conclusion}\label{sect:conc}

We have presented an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters. We applied this method to pairs of low- and high-fidelity models of convection-diffusion-reaction phenomena and were able to obtain QoI estimates with a small relative error without having to solve the inverse problem with the high-fidelity model. In these cases, the localization of the error estimate also indicated regions of the domain that were important to the interaction of the observations and the QoI.

@@

A direction for extension of this work is to the case of the statistical inverse problem. Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization. However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}. One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.

The statistical inverse problem is often solved in a Bayesian framework. Bayes' rule is used to combine a prior distribution, which captures prior beliefs about the parameters, and a likelihood distribution, which captures the likelihood of observations given an instance of the parameter values and a model of noise in the observations, to give a posterior distribution on the parameters. Since there is generally no analytical expression for this posterior distribution, it is usually characterized by samples from the distribution. Sampling methods like the widely-used Markov chain Monte Carlo (MCMC) method require many evaluations of the forward model, and since the number of samples needed grows exponentially with the dimension of the parameter space, this problem becomes intractable for large parameter spaces. In engineering contexts, it is still usually the case, however, that we are ultimately interested in a low-dimensional QoI, and it is the uncertainty in this low-dimensional quantity that we wish to capture; this low-dimensional distribution is referred to as the predictive posterior.

One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled. Such a direction is suggested by the results presented in Section \ref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space. In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution. In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed. Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.

@@

%other directions for extensions that I can't seem to fit in:
%mixing models in time as well? (different mixes of models at different time steps?)
%superadj on intermediate mesh; preliminary results suggest that error estimates remain reasonable and generation of mixed-fidelity models can continue despite the additional approximations to the supplementary adjoint

%\item \Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}. In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model. As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI (NOT TRUE the primary and aux vars appear in the rhs...). When these linearities do not all hold, one cannot obtain an exact error estimate. The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$. As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.

### 2016-09-30 paper/conclusions_v2.tex
renamed paper tex files so that we can do latexdiff on them

A direction for extension of this work is to the case of the statistical inverse problem. Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization. However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}. One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.

@@

One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled. Such a direction is suggested by the results presented in Section \ref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space. In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution. In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed. Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.

>>>>

A direction for extension of this work is to the case of the statistical inverse problem. Thus far in this work, we have considered the deterministic inverse problem, as described in \Cref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization. However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}. One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.

@@

One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled. Such a direction is suggested by the results presented in \Cref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space. In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution. In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed. Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.

### 2016-09-30 paper/intro_v1.tex
renamed paper tex files so that we can do latexdiff on them

In this work, we extend the use of multi-fidelity models to inverse problems. Specifically, we consider the case where there is a target quantity of interest to be computed from the inferred parameters. The use of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; an extension to inverse problems is described in \cite{OdenPrudetal10}. We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest. Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.

The rest of the paper is organized as follows. \Cref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem. Then, in \Cref{sect:alg} we discuss the goal-oriented inference algorithm and present a computational complexity analysis. \Cref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem. Finally, we present conclusions and directions for future work in \Cref{sect:conc}.

>>>>

In this work, we extend the use of multi-fidelity models to inverse problems. Specifically, we consider the case where there is a target quantity of interest to be computed from the inferred parameters. The use of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; an extension to inverse problems is described in \cite{OdenPrudetal10}.\red{\footnote{Vikram, this was known at the time of the thesis, but not not cited in the thesis. I'm not actually sure how to handle this, since this tries to solve the same problem we do, but I don't understand it well enough to do a detailed analysis. I did manage to find the book, if you'd like me to scan the pages to you...}} We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest. Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.

The rest of the paper is organized as follows, \cref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem. Then, in \cref{sect:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis. \cref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem. Finally, we present conclusions and directions for future work in \cref{sect:conc}.

%% \subsection{draft outline}
%% \bit
%% \item background/previous work? to put this work in context?
%%   %this is probably enough? at least for previous work...
%%   %what context though? is this another way to approach inverse problems?
%% \item mathematical formulation
%%   \bit
%%   \item define inverse problem and qoi
%%   \item derive error estimate
%%   \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
%%   \item relation to mesh refinement
%%   \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem? (Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
%%     %solving for adjoint and forward simultaneously (KKT) might cause you to lose an order of accuracy?
%%     %where was that book that Oden might have mentioned inverse application of his method?
%%       %Multiscale methods : bridging the scales in science and engineering / edited by Jacob Fish. (TA335.M85 2010 in barker)
%%   \eit
%% \item numerical results (perhaps not include all of these...)
%%   \bit
%%   \item convection-diffusion(-reaction)
%%     \bit
%%     \item interpretation of error estimate breakdown (interaction of QoI with observations)
%%     \item large reaction term: MF model more cooperative with nonlinear solver
%%     \eit
%%   \item convection-diffusion-reaction, field vs scalar description of parameters
%%     \bit
%%     \item interface question: do we enforce continuity between the two models' parameters?
%%       %-navierstokes+stokes seems to require continuity of flux and velocity across boundary...?
%%       %-is it okay to mix diff and convdiff for the forward like we did? does the discontinuous velocity break any intergration-by-parts   assumptions? (no that's only if discontinuity in diffusion bit...)
%%     \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
%%     %alternative way to describe 'scalar' case? but here we say there is one scalar, so this would be how to combine them...if you wanted plateaus to be different, can let LF model be two-scalars...
%%     %fig 3.10 -> what does the inferred field look like? does it look like two different plateaus?
%%       % practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r4p2_deref/ (pushed 10/3/15)
%%         %at the very last refinement, most of refined region seems to be two large humps...and a section that looks pretty much like the surrounding scalar...so maybe 3 patches...
%%     \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
%%     \eit
%%   \item alternate/additional example: use setup from B+V? navier-stokes and another model?
%%     \bit
%%     \item potential flow? model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
%%     \item there would still be the question of how to interface the models...(in stokes vs navier-stokes foward paper, they just required continuity of state variables (velocity field and presssure))
%%     %do scalar + field for infer BCs on BV NS thing? try for different QoIs? (can we have a variable live on a boundary while the rest are inside? vikram will poke roy about implementing)
%%     %stokes is good in slow flows...not in boundary layer cuz gradient is high...
%%     %what situation would it make sense to use the LF model in some place?
%%     \eit
%%   \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
%%   \eit
%% \item conclusion...what goes in this section usually? summary and directions for future work?
%% \eit

### 2016-09-30 paper/numerical_experiments_v1.tex
renamed paper tex files so that we can do latexdiff on them

\section{Numerical Experiments}\label{sect:numexp}
%
We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}. We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions. In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model. We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
\end{align} 
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by, 
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations). Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in \cref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. 
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. 
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} 
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%
%

We now present the results for solving the inference problem using \cref{alg:refSeries}. Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}. At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement. This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))$, is less than $1\%$.

>>>>

\section{Numerical Experiments}\label{sect:numexp}
%
We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}. We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions. In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model. We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. Finally, in \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings \red{when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}\footnote{\red{Well, compuational savings are only seen in the online-offline case, so that's not the referenced algorithm per se...}}

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
\end{align} 
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by, 
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
-42.0 & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations). Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in \cref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. 
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. 
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} 
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable. The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%
%

We now present the results for solving the inference problem using \cref{alg:refSeries}. Once the QoI error estimate is calculated using \ref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}. At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement. This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))$, is less than $1\%$.
